---
title: "Code Issues"
format: 
  html:
    css: style.css
---

# `T`/`F` Instead of `TRUE`/`FALSE`

## Problem

You are writing the abbreviated forms of `TRUE` and `FALSE`, `T` and `F` or you are using `T` or `F` as names.

## Solution

Change the abbreviation to the full words or use a different variable name.

### Details

In R, `T` and `F` are variables being set to `TRUE` and `FALSE`, respectively. However, those variables can be redefined by the user since these are not reserved words as `TRUE` and `FALSE` are (see the [R Language Definition](https://cran.r-project.org/doc/manuals/r-release/R-lang.html#Reserved-words) for more details). This can result in unexpected code behavior as users of your package might have variables named `T`/`F`.

### Examples

The first example shows that you cannot overwrite `TRUE`:

```{r, error=TRUE}
TRUE <- "Not TRUE anymore"

print(TRUE)
```

This throws an error as `TRUE` is a reserved word and the value of `TRUE` does not change.

`T` (and `F`) on the other hand can be set to a different value:

```{r}
T <- "Not TRUE anymore"

print(T)
```

To avoid any unexpected behaviors and inconsistencies, CRAN reviewers will ask you to write the reserved words, `TRUE` and `FALSE` instead of their abbreviated forms. For the same reason, `T` or `F` should not be used as variable names in your code, examples, tests or vignettes.

------------------------------------------------------------------------

# Issue 2

## Problem

## Solution

### Details

# Issue 3

## Problem

## Solution
