---
title: "Code Issues"
format: 
  html:
    css: style.css
---

# `T`/`F` Instead of `TRUE`/`FALSE` 

## Problem
You are writing the abbreviated forms of `TRUE` and `FALSE`, `T` and `F` or you are using `T` or `F` as names.

## Solution
Change the abbreviation to the full words or use a different variable name. 

## Details

In R, `T` and `F` are variables being set to `TRUE` and `FALSE`, respectively. However, those variables can be redefined by the user since these are not reserved words as `TRUE` and `FALSE` are.
This can result in weird code behavior as users of your package might have variables named `T`/`F`. 

### Examples

The first example shows that you cannot overwrite `TRUE`:
```{r, error=TRUE}
TRUE <- "Not TRUE anymore"
```

This throws an error as `TRUE` is a reserved word. `T` on the other hand can be set to a different value:
```{r}
T <- "Not TRUE anymore"

print(T)
```

`T` can even be set to `FALSE`, completely messing up the functionality of code:

```{r}

T <- FALSE

if(!T) print("T is now FALSE")

```

To avoid any weird behaviors and inconsistencies, CRAN reviews will ask you to write the reserved words, `TRUE` and `FALSE` instead of their abbreviated forms. 





----------------------------------

# Issue 2

## Problem

## Solution

# Issue 3

## Problem

## Solution
