---
title: "Common Issues"
editor: visual
---

# Missing `\value`-tags in .Rd-files

## Problem

Every .Rd file should have an `\value`-tag stating what the output of the function is. Even if nothing is returned, the `\value`-tag is necessary for CRAN.

## Solution

Often it is enough to simply add the missing `\value`-tags. If the function doesn't return anything, write that as your `\value`-tag.

### Details

CRAN wants a `\value`-tag for every .Rd-file containing info about the structure of the output (class) and also what the output means. 
The only exception are .Rd-files for data sets, marked with the `\docType{data}`-tag.

Sometimes functions don't return one specific value but are rather called for their side effects. In that case the `\value`-tag should state this.

```{r, eval=FALSE}
\value{No return value, called for side effects}
```

When using 'roxygen' to render the .Rd-files, an `@return`-tag must be added in the corresponding .R-file. This will create the `\value`-tag automatically when rendering.

```{r}
#' @return What your function returns.
```

For more details on 'roxygen' check the ['roxygen'](occasional.qmd#Re-Render .Rd-files with 'roxygen') section.

# Issue 2

## Problem

## Solution


# Issue 3

## Problem

## Solution